Region-network hierarchical sparsity priors for\\ high-dimensional inference in brain imaging

### 2016-01-24 paper/paper.tex
comment

\section{Introduction}
% sparsity
Many quantitative scientific domains underwent a
recent passage from the classical regime (i.e., ``long data")  to
the high-dimensional regime (i.e., ``wide data")
\cite{jordan2015massive}.
Also in the brain imaging domain,
many contemporary methods for acquiring brain signals yield
more variables per observation than
total observations per data sample.
This high-dimensional scenario challenges many statistical estimators from
classical statistics.
For instance,
the general linear model without additional assumptions
yields an infinity of possible coefficients
and, thus, no solution.
%
Many such ill-posed estimation problems
have become tractable by means of
\textit{sparsity} assumptions
\cite{buhlmann2011statistics, hastie2015statistical}.
Sparsified supervised and unsupervised
learning algorithms have proven to yield
statistical relationships that can be readily
estimated, reproduced, and interpreted
\cite{giraud2014introduction}.
%
Further, \textit{structured sparsity} can impose
domain knowledge on the 
statistical estimation,
thus preassuming the variables to have unequal importance
and to obey expected data distributions
\cite{bach2012optimization}.
Yet, what neurobiological structure suggests itself
to harness the
\textit{curse of dimensionality} with
$\textgreater$100,000 variables
in neuroimaging research?

>>>>

\section{Introduction}
% sparsity
Many quantitative scientific domains underwent a
recent passage from the classical regime (i.e., ``long data")  to
the high-dimensional regime (i.e., ``wide data")
\cite{jordan2015massive}.
Also in the brain imaging domain,
many contemporary methods for acquiring brain signals yield
more variables per observation than
total observations per data sample.
This high-dimensional scenario challenges many statistical estimators from
classical statistics.
For instance,
the estimation of any generalized linear model without additional assumptions
becomes underdetermined, i.e. yields full subspace of possible solutions, many or most of which will not generalize well in a predictive setting.
%
Many such ill-posed estimation problems
have benefited from
\textit{sparsity} assumptions
\cite{buhlmann2011statistics, hastie2015statistical}, which act as a 
regularizer and can be used for model selection.
Sparse supervised and unsupervised
learning algorithms have proven to yield
statistical relationships that can be readily
estimated, reproduced, and interpreted
\cite{giraud2014introduction}.
%
Generally, \textit{structured sparsity} can impose
domain knowledge on the 
statistical estimation,
thus preassuming the variables to have unequal importance
and to obey expected data distributions
\cite{bach2012optimization}.
{\color{red}Michael: This is the definition of a prior, not of strutured sparsity}
Yet, what neurobiological structure suggests itself
to harness the
\textit{curse of dimensionality} with
$\textgreater$100,000 variables
in neuroimaging research?
